Big Ideas in Sports Analytics and Statistical Tools for their Investigation

### 2022-06-30 sports_analytics.Rmd
added wp plot using `nflfastR`

(add a wp example from nflfastR or nflscapr)

>>>>

Figure \ref{fig:nflfastr_wp}

```{r}
# win prob for Minneapolis Miracle
library(teamcolors)

vikings <- teamcolors |> 
  filter(league == "nfl", name == "Minnesota Vikings") |> 
  pull(primary)

saints <- teamcolors |> 
  filter(league == "nfl", name == "New Orleans Saints") |> 
  pull(primary)
```

```{r nflfastr_wp, fig.cap="WP for MIN vs NO (add more later)"}
library(nflfastR)
load_pbp(2017) |> 
  filter(season_type == "POST",
         home_team == "MIN",
         away_team == "NO",
         !is.na(home_wp),
         !is.na(away_wp)) |>
  select(game_seconds_remaining, home_wp, away_wp) |> 
  pivot_longer(!game_seconds_remaining,
               names_to = "team",
               values_to = "wp") |> 
  ggplot(aes(game_seconds_remaining, wp, color = team)) +
  geom_line(size = 2) +
  scale_x_reverse(breaks = seq(0, 3600, 900)) + 
  scale_color_manual(values = c(saints, vikings), 
                     labels = c("New Orleans Saints", "Minnesota Vikings")) +
  # geom_hline(yintercept = 0.5, color = "gray", linetype = "dashed") +
  # geom_vline(xintercept = seq(0, 2700, 900), linetype = "dashed", color = "gray") + 
  labs(x = "Time Remaining (seconds)",
       y = "Win Probability",
       color = NULL) +
  theme_bw() +
  theme(legend.position = "top")
```
